---
title: "Yoshita Aligina HW 2"
output: html_notebook
---
1. Is it appropriate to use linear regression models to address each question in the following? Why
and why not?
(a) We COULD use linear regression models here in the case when we try to predict this using biological sex as a binary variable. However, this may not work if sex and age at death do not have a linear relationship.
(b) I do not think it would be appropriate at all because the idea is people either do or don't have diabetes, there isn't an in between. 
(c) We couldn't because we are expecting continuous results, which we would not receive in this sitution. 
(d) We could not because we are given three categoricaa values for the quality of the wine. 


```{r}
library(foreign)
kidiq=read.dta("kidiq.dta")

```

2. 
(a) In Code
(b) In Code
(c) The slope indicates the expected increase in  score for children whose moms completed high school.
(d) The intercept represents the average kid score for children whose moms did not complete high school.
```{r}
#(a)
boxplot(kidiq$kid_score ~ kidiq$mom_hs, 
        xlab = "Mom HS (0 = No, 1 = Yes)", 
        ylab = "Kid Score", 
        main = "Boxplot of Kid Score by Mom HS")
#(b)
lm_model <- lm(kid_score ~ mom_hs, data = kidiq)
summary(lm_model)$coefficients

```

3.Split the data into two subgroups, corresponding to mom hs=0 and mom hs=1 respectively. For
each subgroup, use the Kid’s Score (kid score) and Mom’s Score (mom iq) as the response and
predictor respectively, and do the following:
(a) In Code
(b) In Code
(c) For both groups, the slope represents the expected increase in the kid's score for how much higher the mother's IQ is, it is proportional. 
```{r}
#(a & b)
lm_0 <- lm(kid_score ~ mom_iq, data = subset_0)
lm_1 <- lm(kid_score ~ mom_iq, data = subset_1)

summary(lm_0)$coefficients
summary(lm_1)$coefficients

plot(subset_0$mom_iq, subset_0$kid_score, 
     xlab = "Mom IQ", ylab = "Kid Score", 
     main = "Mom HS = 0")
abline(lm_0, col = "blue")

plot(subset_1$mom_iq, subset_1$kid_score, 
     xlab = "Mom IQ", ylab = "Kid Score", 
     main = "Mom HS = 1")
abline(lm_1, col = "blue")

```

